---
title: "Explore the structure of SSNAPStats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explore the structure of SSNAPStats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.width = 7,
                      fig.height = 7,
                      fig.align = "center")
```

## About the SSNAP R packages

SSNAPStats is a package designed to produce statistics from national
audit data. It is specifically designed around Stroke Sentinel
National Audit data (see <http://www.strokeaudit.org>), but recent
developments have made it sufficiently generic to be potentially
applicable to other audits in future.

SSNAPStats is part of a group of packages for processing SSNAP data:

```{r package_graph, echo=FALSE}
DiagrammeR::DiagrammeR("graph TB;
  A>Raw SSNAP Data]-->B(SSNAPInterface);
  B-->C(SSNAPStats);
  C-->E(SSNAPReports);
  D(SSNAPCharts)-->E;
  D-->F((SSNAP Dashboard));
  C-->F")
```


- [SSNAPInterface](https://ssnap.github.io/SSNAPInterface/) loads raw
CSV file data.
- [SSNAPStats](https://ssnap.github.io/SSNAPStats/) processes loaded
SSNAP data, organises the data into cohorts and prepares aggregated
data for reporting.
- [SSNAPCharts](https://ssnap.github.io/SSNAPCharts/) provides
generic report outputs for reports.
- [SSNAPReports](https://ssnap.github.io/SSNAPReports/) produces
reports from SSNAP data.
- [SSNAPDashboard](https://ssnap.github.io/SSNAPDashboard/) is a
Shiny-based application for realtime SSNAP data analysis.

## How does SSNAPStats analyse audit data?

SSNAPStats breaks down the audit processing into a set of key
steps:

```{r object_graph, echo=FALSE}
DiagrammeR::DiagrammeR("graph TB;
  A(cohorts)-->D{create_cohort};
  B(audit_measure)-->C(audit_output_spec);
  C-->D")
```


The first step is to set up rules to produce a definition of the 
**cohorts** you want to use. Cohorts are time series-orientated
collections of patient records.

The second stage is to set up rules to produce **audit measures**.
These rules produce either discrete results (ie. counts of a
particular value, or proportions of patients meeting or not meeting a
condition,) or they may be continuous (ie. to create median values).

Different outputs of results from an audit require different
levels of detail: the more detail you request the longer it takes to
process. An **audit output specification** is used to produce a list
of the audit measures you want, alongside how much detail from each
measure in the list, without having to re-write the same measure
multiple times to get different levels of detail for different
purposes.

Finally we use the **create_cohort()** function to apply the cohort
definition with the audit output specification to produce the results.

## Shortcuts to make routine SSNAP data analysis easier

So far the process we have described is applicable to all audits.
With SSNAP, there are predefined cohort definitions, and predefined
lists of audit measures that are used for routine published analysis.

To make things simpler, there are a set of lists and functions, all
prefixed with **ssnap_**, that make handling routine data easier.
These use pre-built cohorts and measures within the package. There
are also functions to build a 'ssnapScores' table - which takes
aggregated data from multiple cohorts and produces the scored reports
seen in published SSNAP data. These functions are all built using the
lower level generic functions described earlier.

- **ssnap_field** is a named list of 'record level' expressions (such
as time differences). These are inserted into audit measures to make
the code easier to read and/or reduce duplication.
- **ssnap_measures** is a named list of audit measures used in SSNAP.
- **ssnap_cohort_definitions** is a named list of cohort definitions.
- The **ssnap_audit_output_specs.R file** defines a set of audit
output specifications for cohorts used in SSNAP analysis. Each one of
these is a tibble.
- **ssnap_cohorts** is a simplified version of the **create_cohort**
functions. It creates cohorts using the pre-defined cohorts and
measures.

SSNAP reporting periods have changed over time from three monthly to
four monthly and back again; therefore there are also definitions for
the reporting periods and annual report periods for time series
analysis and filtering.
