---
title: "Use SSNAPStats to create output data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use SSNAPStats to create output data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.width = 7,
                      fig.height = 7,
                      fig.align = "center")
library(tibble)
library(ssnapstats)
```

## Using the Fake Hospital Dataset

The Fake Hospital dataset is not currently designed for any serious
use beyond examples and testing code. Ideally a more complete and
realistic dataset would allow more complex ideas to be demonstrated.
We will however use it to demonstrate the functions throughout this
vignette.

You can access this dataset as a tibble using the command:

```{r ssnap_fake_data, eval = FALSE}
ssnap_fake_data
```

The raw output from ssnap_fake_data looks like this:

```{r print_ssnap_fake_data, rows.print = 10}
ssnap_fake_data
```

## Fetch a pre-built SSNAP cohort

SSNAPStats has a set of 'high level' functions for dealing with
known SSNAP cohorts and measures sets to save you having to write
functions picking the correct cohort and measures list.

Please note that the data from the Fake Hospital dataset is very
incomplete so the values are not representative and in many cases will
be missing.

```{r show_a_ssnap_cohort}
testCohort <- ssnap_cohorts(ssnap_data = ssnap_fake_data,
                            cohort = "Team72HrCohortKIs",
                            period_type = "months",
                            aggregate_by = "team")
```

To get a full list of available cohorts, look at the
\code{ssnap_cohort_names} vector for available values (the help file
describes more completely each cohort):

```{r show ssnap_cohort_names}
ssnap_cohort_names
```

